\documentclass[11pt]{ist-thesis-lt}
\usepackage{multirow}
\usepackage{booktabs}
%\pagestyle{bachelorthesis}  % 卒論
%\pagestyle{ebachelorthesis}  % Graduation Thesis
%\pagestyle{masterthesis}  % 修論（目安;38ページ以上）
\pagestyle{emasterthesis}  % Master Thesis
%\pagestyle{draft}  % 未完成ドラフト
%\pagestyle{edraft}  % Draft

\title{論文のタイトル\\タイトル2行目}
\author{論文 太郎}
\supervisor{?? 教授}
%\supervisor{Professor ??}
\deadline{令和?年?月?日} % 正規の提出期日
%\deadline{February Xth, XXXX}

\begin{document}

\titlepage{}

% タイトル中に改行が含まれる場合は，改行を取り除いたタイトルを再定義
\title{論文タイトル}

\abstract{
ここに概要を書く
}

\keyword{
  \hspace{7mm} 論文のキーワードその1\\
  \hspace{7mm} 論文のキーワードその2\\
  \hspace{7mm} 論文のキーワードその3\\
}

% 目次を出力
\toc{}

% 本文開始
\section{Introduction}

\subsection{Research Background}
Open-source software (OSS) ecosystems have become an indispensable digital foundation for modern society. A vast majority of software development, corporate operations, and academic research worldwide depend directly or indirectly on these OSS projects.

However, existing literature reports that many OSS projects rely heavily on the dedicated contributions of a small number of ``core developers''\cite{sample}. Core developers are defined as a key group of contributors who possess deep technical knowledge of the project and hold the authority to make significant changes to the source code. Even in large-scale projects, the developers responsible for the most critical parts of the codebase are often extremely limited in number\cite{sample}. This structure entails an inherent vulnerability: the departure or burnout of these core developers can lead directly to the stagnation or termination of the project.

This structural vulnerability gained significant public attention following severe security incidents such as Heartbleed (OpenSSL)\cite{sample} and Log4Shell (Log4j)\cite{sample}. The fact that software underpinning global infrastructure is maintained by a handful of volunteers has highlighted a critical lack of sustainability in the modern digital ecosystem\cite{sample}.

\subsection{Motivation and Problem Statement}
To address these sustainability challenges, funding platforms such as Open Collective\cite{sample} and GitHub Sponsors\cite{sample} have emerged, allowing projects to solicit financial support directly. These platforms provide a mechanism to inject external capital into activities that were previously performed on a purely volunteer basis, thereby supporting stable project management.

In theory, OSS projects are maintained by voluntary contributions. However, if these projects increasingly depend on external funding for continuous maintenance and development, the cessation of such funds could jeopardize the longevity of the projects and, by extension, the health of the entire ecosystem that relies on them.

While many projects are now receiving significant financial contributions, the specific impact of these funds on actual software development activities remains poorly understood. Specifically, the correlation and causal relationships between funding and development productivity have not yet been sufficiently quantified.

\subsection{Research Objectives}
The objective of this research is to investigate the relationship between external funding and software development activities in OSS projects based on empirical data. Specifically, we address the following three Research Questions:

\begin{enumerate}
    \item \textbf{RQ1: Investigation of Financial Contributions.} Why are they funding these open-source projects? How much are they donating?
    \item \textbf{RQ2: Analysis of Funding Expenditures.} For what purposes (e.g., engineering, marketing, or operations) do projects spend the funds they receive?
    \item \textbf{RQ3: Quantitative Measurement of Impact on Development.} How do the acquisition and expenditure of funds correlate with GitHub development activities, such as the number of pull requests, commits, and active developers?
\end{enumerate}

\subsection{Methodology Overview}
In this study, we utilize the Open Collective API\cite{sample} to collect the complete transaction histories of target OSS projects. This dataset includes granular metadata such as expenditure purposes, transaction amounts, and timestamps.

Next, we correlate this financial data with GitHub contribution histories to analyze changes in development activity before and after the acquisition of funds or specific expenditures (e.g., payments for engineering tasks). Through this approach, we verify whether the injection of capital directly contributes to more active maintenance and development.

\subsection{Significance of the Research}
The projects targeted in this study are critical OSS infrastructures used by companies, organizations, and researchers worldwide. If it is revealed that these projects rely heavily on donations for their maintenance, it will provide crucial insights into the potential risks and vulnerabilities of the global software ecosystem.

The findings of this research will provide essential guidelines for developer communities seeking sustainability, companies dependent on OSS, and funding platform operators to evaluate the effectiveness of financial support and the overall health of projects.

\section{Background and Related Work}

\subsection{OSS Sustainability and Core Developers}

The sustainability of open-source software (OSS) is a critical concern as modern society increasingly relies on these projects as a digital foundation\cite{sample}. However, research has shown that many OSS projects suffer from a high concentration of knowledge, relying on a very small group of core developers. 

To quantify this risk, the ``Truck Factor'' metric\cite{sample} was proposed to represent the minimum number of developers who must leave a project before it becomes incapacitated\cite{sample}. Empirical studies on popular GitHub repositories have revealed that 65\% of these projects have a Truck Factor of two or less\cite{sample}. Furthermore, a large-scale study of over 36,000 projects found that 89\% of projects have experienced the loss of their core development team at least once, with 70\% of these abandonments occurring within the first three years of the project's life\cite{sample}. Only 27\% of projects that lose their core team are able to survive and attract new core developers\cite{sample}.

The danger of this structural vulnerability is well illustrated by high-profile security incidents. The Log4Shell vulnerability in the Log4j library exposed how critical global infrastructure was maintained by uncompensated volunteers, some of whom worked 22-hour shifts to mitigate the crisis\cite{sample}. Similarly, the Heartbleed incident in OpenSSL revealed that a project securing the majority of the internet was operating on an annual donation budget of only US\$2,000, with only one full-time developer\cite{sample}. These cases highlight the urgent need for external funding to support core developers and ensure long-term sustainability\cite{sample}.

\subsection{Funding in Open-source Ecosystems}
The emergence of platforms like Open Collective has introduced unprecedented transparency to the financial management of open-source projects by making all transactions publicly visible. While corporate entities tend to provide larger individual donations, individual contributors are essential for long-term sustainability\cite{sample}, as they often provide higher total funding and demonstrate greater stickiness through recurring support\cite{sample}. However, projects like OpenSSL illustrate that reliance on grassroots funding alone can be insufficient for critical infrastructure, often resulting in chronic underfunding until a major crisis occurs.

Although a positive correlation has been observed between corporate donation levels and project maintenance activity, the specific impact of diverse expenditure types on development productivity remains poorly understood. This study addresses this research gap by quantitatively analyzing the relationship between these financial flows and GitHub development metrics.

\subsection{Empirical Studies on Development Activity}
To evaluate the impact of external events on OSS projects, researchers typically utilize established repository metrics. Indicators such as the number of commits and pull requests (PRs) are widely accepted as proxies for development activity and productivity. Additionally, community metrics such as stars and forks are used to measure project popularity and visibility.

Studies focusing on social media exposure, such as promotion on Hacker News, have demonstrated that increased visibility can lead to a significant spike in forks, stars, and the number of contributors shortly after the project is mentioned\cite{sample}. Research has also indicated that projects receiving positive community sentiment through these platforms exhibit higher growth in commits and PRs\cite{sample}. This study builds upon these established empirical methods to investigate whether the injection of financial resources through funding platforms leads to similar quantifiable improvements in development activity.

\section{(DRAFT) Progress and Results}

\subsection{About the Mined Data}
The mined data is stored in the following three SQL tables.

\begin{table}[htbp]
    \centering
    \caption{List of Tables}\label{tab:tables-summary}
    \begin{tabular}{ll}
        \toprule
        Name & Description \\
        \midrule
        \texttt{collective\_transactions} & Table containing income and expenditure data for collectives \\
        \texttt{collectives}             & Table containing general information about collectives \\
        \texttt{commit\_history}          & Table containing commit history \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{Columns for Each Table}
(This section summarizes the research data collected to the present.)
The columns for the three SQL tables are shown in Table~\ref{tab:collective-transactions-columns},~\ref{tab:collectives-columns}, and~\ref{tab:commit-history-columns}.

\begin{table}[htbp]
    \centering
    \caption{Columns of \texttt{collective\_transactions}}\label{tab:collective-transactions-columns}
    \begin{tabular}{ll}
        \toprule
        Column Name & Meaning \\
        \midrule
        \texttt{amount\_value}        & Transaction amount \\
        \texttt{amount\_currency}     & Currency \\
        \texttt{created\_at}          & Transaction timestamp \\
        \texttt{expense\_tags}        & Expense categories (natural language) \\
        \texttt{type}                & debit or credit (distinguishing income and expenditure) \\
        \texttt{kind}                & \begin{tabular}{l}
            Transaction type (distinguishing fund receipt, \\ 
            fund usage, or fee payment)
        \end{tabular} \\
        \texttt{description}         & Description (natural language) \\
        \texttt{id}                  & ID \\
        \texttt{from\_account\_name}  & Sender's name \\
        \texttt{from\_account\_type}  & Sender's account type \\
        \texttt{to\_account\_slug}    & Recipient's slug (unique identifier string) \\
        \texttt{to\_account\_name}    & Recipient's name \\
        \texttt{to\_account\_type}    & Recipient's account type \\
        \texttt{expense\_type}        & Payment type (the form in which the payment occurred) \\
        \texttt{expense\_description} & Expense description (natural language) \\
        \texttt{from\_account\_slug}  & Sender's slug (unique identifier string) \\
        \texttt{project\_slug}        & Project slug (unique identifier string) \\
        \texttt{project\_name}        & Project name \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table}[htbp]
    \centering
    \caption{Columns of \texttt{collectives}}\label{tab:collectives-columns}
    \begin{tabular}{ll}
        \toprule
        Column Name & Meaning \\
        \midrule
        \texttt{total\_spent\_value}     & Cumulative expenditure to date \\
        \texttt{total\_spent\_currency}  & Currency \\
        \texttt{social\_links}           & Links to social media (Website, GitHub, Twitter, etc.) \\
        \texttt{yearly\_budget\_value}   & Estimated yearly budget (funds to be received) \\
        \texttt{yearly\_budget\_currency}& Currency \\
        \texttt{balance\_value}          & Current balance \\
        \texttt{balance\_currency}       & Currency \\
        \texttt{created\_at}             & Registration date \\
        \texttt{total\_received\_value}  & Total amount received to date \\
        \texttt{total\_received\_currency}& Currency \\
        \texttt{twitter\_handle}         & Twitter handle \\
        \texttt{id}                      & Collective ID \\
        \texttt{github\_account}         & GitHub account \\
        \texttt{slug}                    & Collective slug \\
        \texttt{name}                    & Collective name \\
        \texttt{type}                    & Type (e.g., collective, project) \\
        \texttt{description}             & Description \\
        \texttt{website}                 & Website URL \\
        \texttt{github\_handle}          & GitHub handle \\
        \bottomrule
    \end{tabular}
\end{table}

\begin{table}[htbp]
    \centering
    \caption{Columns of \texttt{commit\_history}}\label{tab:commit-history-columns}
    \begin{tabular}{ll}
        \toprule
        Column Name & Meaning \\
        \midrule
        \texttt{author\_name}    & Person who authored the commit \\
        \texttt{author\_email}   & Author's email address \\
        \texttt{author\_time}    & Timestamp when the commit was originally authored \\
        \texttt{committer\_name} & Person who committed/edited the commit \\
        \texttt{committer\_email}& Committer's email address \\
        \texttt{commit\_time}    & Timestamp when the commit was recorded (e.g., via rebase) \\
        \texttt{mined\_at}       & Timestamp when the data was mined \\
        \texttt{repo\_path}      & Repository path \\
        \texttt{subject}         & Commit message subject \\
        \texttt{body}            & Commit description (body) \\
        \texttt{repo\_name}      & Repository name \\
        \texttt{commit\_hash}    & Commit hash \\
        \texttt{parent\_hashes}  & Parent commit hashes \\
        \bottomrule
    \end{tabular}
\end{table}

\subsection{RQ1: Investigation of Financial Contributions}
There are no answers to RQ1 yet.
We are considering how to answer RQ1.

\subsection{RQ2: Analysis of Funding Expenditures}
We categorized how collectives utilize the funds they receive. 
Two possible approaches for this classification are rule-based and machine-learning-based. 
In this study, we employed rule-based classification. 
Table~\ref{tab:expenditures-summary-with-subtotals} presents the record count and total expenditure for each Recipient\_Category and Purpose.

\begin{table}[htbp]
    \centering
    \caption{Breakdown of Expenditures by Rule-Based Labeling}\label{tab:expenditures-summary-with-subtotals}
    \begin{tabular}{llrr}
        \toprule
        Recipient Category & Purpose & Transaction Count & Amount (USD) \\
        \midrule
        \multirow{3}{*}{Individual} & \texttt{Individual other} & 14,265 & $-5,496,780.13$ \\
        \cmidrule(r){2-4}
        & \texttt{Compensation} & 18,488 & $-31,702,794.38$ \\
        \cmidrule(r){2-4}
        & \textbf{Subtotal} & \textbf{32,753} & \textbf{$-37,299,574.51$} \\
        \midrule
        \multirow{5}{*}{Organization} & \texttt{Marketing} & 18 & $-8,195.49$ \\
        \cmidrule(r){2-4}
        & \texttt{Infrastructure} & 119 & $-269,162.02$ \\
        \cmidrule(r){2-4}
        & \texttt{Governance} & 31 & $-277,295.79$ \\
        \cmidrule(r){2-4}
        & \texttt{Organization other} & 3,876 & $-15,590,876.88$ \\
        \cmidrule(r){2-4}
        & \textbf{Subtotal} & \textbf{4,044} & \textbf{$-16,145,530.18$} \\
        \midrule
        \multirow{2}{*}{Other} & \texttt{Unknown} & 30 & $-4,924.64$ \\
        \cmidrule(r){2-4}
        & \textbf{Subtotal} & \textbf{30} & \textbf{$-4,924.64$} \\
        \midrule
        \multirow{4}{*}{Vendor} & \texttt{E-commerce} & 159 & $-44,086.03$ \\
        \cmidrule(r){2-4}
        & \texttt{Cloud or SaaS} & 1,959 & $-181,326.89$ \\
        \cmidrule(r){2-4}
        & \texttt{Vendor other} & 4,448 & $-4,360,332.87$ \\
        \cmidrule(r){2-4}
        & \textbf{Subtotal} & \textbf{6,566} & \textbf{$-4,585,745.79$} \\
        \midrule
        \multicolumn{2}{l}{\textbf{Grand Total}} & \textbf{43,393} & \textbf{$-58,035,775.12$} \\
        \bottomrule
    \end{tabular}
\end{table}


\subsection{RQ3: Quantitative Measurement of Impact on Development}
(This section will summarize data from past experiments.)
\\
For each collective, we examined changes in the number of commitments over 30 days and 180 days before and after the peak funding period.
\\
A chart will be included here.

\acknowledgement{
ここに謝辞を書く
}

% 参考文献を出力
\bibliographystyle{jplain}
\bibliography{reference}

\end{document}
